Redshift evolution of the SN stretch distribution

### 2019-10-31 Nicolas.tex
Little changes

\documentclass{aa}
\usepackage{preambule}
\usepackage[varg]{txfonts}

@@

@@

\begin{table}[htbp!]
    \centering
    \caption{Number of SNe Ia effectively used for each survey, totalling 689
    Sne Ia. TO CORRECT FOR NEW ZMAX}
    \label{tab:sample}
    \begin{tabularx}{\linewidth}{|Y*{1}{|Y}|}\hline
        \rowcolor{gray!15} Survey & Number of SNe Ia \\\hline\hline
        SNf & 141 \\\hline
        PS1 & 178 \\\hline
        SDSS & 206 \\\hline
        SNLS & 138 \\\hline
        HST & 26 \\\hline
    \end{tabularx}
\end{table}

\begin{figure}[htbp!]
    \centering
    \subfigure[Method]{\label{fig:zdet}
        \includegraphics[width=\linewidth]{Article_figures/zmax_determination.pdf}}
    \subfigure[Result]{\label{fig:surveys_cuts}
    \includegraphics[width=\linewidth]{Article_figures/surveys_cuts_x.pdf}}
    \caption{(a) $z\St{max}$ determination from the interpolated poissonian
    evolutions; (b) SDSS, SNLS and PS1 samples cut at $z\St{max}$ as explained in
    section \ref{sec:sam}. The data we use is in plain markers.}
\end{figure}

@@

\begin{figure}[htbp!]
    \centering
    \subfigure[Raw data]{\label{fig:snf_data}
        \includegraphics[width=\linewidth]{Article_figures/BiGaussian_onlydata.pdf}}
    \subfigure[First implemented model]{\label{fig:3G2M2SSNF}
        \includegraphics[width=\linewidth]{Article_figures/BiGaussian.pdf}}
    \caption{Stretch des supernovae étudiées par la collaboration SNF en
    fonction de log(LsSFR). La couleur représente la probabilité pour une
supernova d'être issue d'un jeune progéniteur.}
    \label{fig:mod_first}
\end{figure}

@@

We implemented and compared 10 models in total, 4 of which have an
evolution with the redshift from $\de\z$, and 6 don't ($\de\z = f =
\mathrm{cst}$). The ones with and evolution are:
\begin{itemize}
    \item 3G2M2S, the one we described (but fitted on all the data);
    \item 3G2M1S, where this time $\s_1 \equiv \s_2$;
    \item 2G2M2S, model taken from HOWELL 2009 where we added $\de\z$;
    \item 3G3M3S, with three independent gaussians.
\end{itemize}
The ones without a stretch evolution are the same ones but with an "F" implying
we set $\de\z = f = \mathrm{cst}$, and two others:
\begin{itemize}
    \item 1G1M1S, where there is no distinction between old and young SNe;
    \item 1G1M2S, taken from KESLLER 2017 and used in recent cosmological
        analysis SCOLNIC 2018. It's an asymetric model where
\end{itemize}

\begin{align}
 p(x_1^i, \d x_1^i | \m, \s_-, \s_+) = 
    \begin{cases}
        \mathcal{N} \LF{\m, \sqrt{\s_-{}^2 + \d x_1^i{}^{2}}} (x_1^i) & \text{if
        } x_1^i\geq \m\\
        \mathcal{N} \LF{\m, \sqrt{\s_+{}^2 + \d x_1^i{}^{2}}} (x_1^i), &
        \text{else}
    \end{cases}
\end{align}

@@

\begin{table}[htbp!]
    \centering
    \caption{Valeurs des paramètres pour différents modèles. En rouge les
    données aberrantes.}
    \label{tab:val}
    \begin{tabularx}{\linewidth}{|Y*{6}{|Y}|}\hline

        \rowcolor{gray!15} Modèle & $a$ & $f$ & $\m_1$ & $\s_1$ & $\m_2$ &
        $\s_2$ \\\hline\hline

        3G2M2S$_{\mathrm{SNf}}$ & $0.48 \pm 0.07$ & none & $0.39 \pm 0.07$ &
        $0.56 \pm 0.05$ & $-1.5 \pm 0.1$ & $0.52 \pm 0.09$ \\\hline

        3G2M2S & $0.48 \pm 0.17$ & none & $0.36 \pm 0.08$ & $0.61 \pm 0.05$ &
        $-1.3 \pm 0.2$ & $0.60 \pm 0.12$ \\\hline

        3G2M2SF & \textcolor{red}{$0.1 \pm 0.6$} & \textcolor{red}{$0.2 \pm
        0.6$} & $-0.9 \pm 0.7$ & $0.7 \pm 0.3$ & $0.5 \pm 0.2$ & $0.6 \pm 0.1$
        \\\hline

        3G2M1S & $0.47 \pm 0.07$ & none & $0.35 \pm 0.04$ & $0.61 \pm 0.03$ &
        $-1.25 \pm 0.10$ & $\s_1$ \\\hline

        3G2M1SF & \textcolor{red}{$0.2 \pm 0.9$} & $0.7 \pm 0.3$ & $0.36 \pm
        0.04$ & $0.60 \pm 0.03$ & $-1.23 \pm 0.10$ & $\s_1$ \\\hline

        2G2M2S & none & none & $0.49 \pm 0.04$ & $0.54 \pm 0.03$ & $-0.72 \pm
        0.08$ & $0.83 \pm 0.07$ \\\hline

@@

    \end{tabularx} \bigbreak

\begin{tabularx}{\linewidth}{|Y*{2}{|Y}|}\hline

    \rowcolor{gray!15} Modèle & $\m$ & $\s$ \\\hline\hline

@@

\end{tabularx} \bigbreak

\begin{tabularx}{\linewidth}{|Y*{3}{|Y}|}\hline

    \rowcolor{gray!15} Modèle & $\m$ & $\s_-$ & $\s_+$ \\\hline\hline

@@

\end{tabularx} \bigbreak

\begin{tabularx}{\linewidth}{|Y*{8}{|Y}|}\hline

    \rowcolor{gray!15} Modèle & $a$ & $f$ & $\m_1$ & $\s_1$ & $\m_2$ & $\s_2$ &
    $m_3$ & $\s_3$ \\\hline\hline

    3G3M3S & $0.14 \pm 0.08$ & none & $0.51 \pm 0.06$ & $0.54 \pm 0.04$ & $-1.9
    \pm 0.2$ & $0.29 \pm 0.11$ & $-0.55 \pm 0.12$ & $0.67 \pm 0.15$ \\\hline

@@

\end{tabularx} \bigbreak

\end{table}

\section{Results}
To compare all these models, we use the Akaike Information Criterion corrected
for sample size (BURNHAM 2002), that penalises the increase of free parameters
in order to discourage overfitting:
\begin{equation}
    \mathrm{AICc} = \mathrm{AIC} + \LR{2k\LF{k+1}}{n - k - 1}
\end{equation}
with $\mathrm{AIC} = 2k - 2\ln\LF{\mathcal{L}}$, where $k$ is the number of free
parameters and $\Lc$ the likelihood. The probability for a model to be as
representative as the "best" one is given by:
\begin{equation}
    p(\mathrm{other} > \mathrm{best}) = \exp\LF{\D\mathrm{AICc}/2}
\end{equation}
As such, we obtain the results table \ref{tab:comp}.

\begin{table}[htbp!]
    \centering
    \caption{Comparaison des modèles. NR représente les modèles implémentés
             durant ce stage. (F) indique les modèles pour lesquels il n'y a pas
             d'évolution de la fraction de SNe~Ia jeunes et vieilles en fonction
             du redshift.}
    \label{tab:comp}
    \begin{tabularx}{\linewidth}{|Y*{6}{|Y}|}\hline

        \rowcolor{gray!15} Name & Description & Free param &
        $\ln\mathcal{L}$ & $AICc$ & $\D AICc$ & Proba \\\hline\hline

        3G2M1S & NR 1S & 4 & 1815 & 1823 & 0.0 & $1.0$ \\\hline

        3G2M2S & NR 2S & 5 & 1815  & 1825 & -2.0 & $3.6\times10^{-1}$ \\\hline

        2G2M2S & Howell & 4 & 1818  & 1826 & -3.4 & $1.8\times10^{-1}$ \\\hline

        3G3M3S & NR 3S & 7 & 1812  & 1826 & -3.6 & $1.6\times10^{-1}$ \\\hline

        3G3M3SF & NR 3S (F) & 8 & 1813 & 1829 & -6.3  & $4.3\times10^{-2}$
        \\\hline

        2G2M2SF & Howell (F) & 5 & 1823  & 1833 & -9.9 & $7.0\times10^{-3}$
        \\\hline

        3G2M1SF & NR 1S (F) & 5 & 1823  & 1833 & -10.4 & $5.5\times10^{-3}$
        \\\hline

        3G2M2SF & NR 2S (F) & 6 & 1823  & 1835 & -12.0 & $2.5\times10^{-3}$
        \\\hline

        1G1M2S & Kessler (F) & 3 & 1837  & 1843 & -20.2 & $4.1\times10^{-5}$
        \\\hline

@@

    \end{tabularx}
\end{table}

We find that every model lacking an evolution of the stretch with the redshift
is systematically worse than those that implement it.

>>>>

\documentclass{aa}
\usepackage{preambule}
\usepackage{graphicx}
\usepackage[varg]{txfonts}

@@

\begin{figure*}[htbp!]
    \centering
    \subfigure[Method]{\label{fig:zdet}
        \includegraphics[width=8.5cm]{Article_figures/zmax_determination.pdf}}
    \subfigure[Result]{\label{fig:surveys_cuts}
    \includegraphics[width=8.5cm]{Article_figures/surveys_cuts_x.pdf}}
    \caption{(a) $z\St{max}$ determination from the interpolated poissonian
    evolutions; (b) SDSS, SNLS and PS1 samples cut at $z\St{max}$ as explained in
    section \ref{sec:sam}. The data we use is in plain markers.}
\end{figure*}

@@

\begin{table}[htbp!]
    \centering
    \caption{Number of SNe Ia effectively used for each survey, totalling 689
    Sne Ia. TO CORRECT FOR NEW ZMAX}
    \label{tab:sample}
    \begin{tabular}{c c}\hline
        \rowcolor{gray!15} Survey & Number of SNe Ia \\\hline
        SNf & 141 \\
        PS1 & 178 \\
        SDSS & 206 \\
        SNLS & 138 \\
        HST & 26 \\\hline
    \end{tabular}
\end{table}

@@

\begin{figure*}[htbp!]
    \centering
    \subfigure[Raw data]{\label{fig:snf_data}
        \includegraphics[width=8.5cm]{Article_figures/BiGaussian_onlydata.pdf}}
    \subfigure[First implemented model]{\label{fig:3G2M2SSNF}
        \includegraphics[width=8.5cm]{Article_figures/BiGaussian.pdf}}
    \caption{Stretch des supernovae étudiées par la collaboration SNF en
    fonction de log(LsSFR). La couleur représente la probabilité pour une
supernova d'être issue d'un jeune progéniteur.}
    \label{fig:mod_first}
\end{figure*}

@@

We implemented and compared 10 models in total, 4 of which have an
evolution with the redshift from $\de\z$, and 6 don't ($\de\z = f =
\mathrm{cst}$). The ones with and evolution are:
\begin{itemize}
    \item 3G2M2S, the one we described (but fitted on all the data);
    \item 3G2M1S, where this time $\s_1 \equiv \s_2$;
    \item 2G2M2S, model taken from HOWELL 2009 where we added $\de\z$;
    \item 3G3M3S, with three independent gaussians.
\end{itemize}
The ones without a stretch evolution are the same ones but with an "F" implying
we set $\de\z = f = \mathrm{cst}$, and two others:
\begin{itemize}
    \item 1G1M1S, where there is no distinction between old and young SNe;
    \item 1G1M2S, taken from KESLLER 2017 and used in recent cosmological
        analysis SCOLNIC 2018. It's an asymetric model where
\end{itemize}
\begin{align}
 p(x_1^i, \d x_1^i | \m, \s_-, \s_+) = 
    \begin{cases}
        \mathcal{N} \LF{\m, \sqrt{\s_-{}^2 + \d x_1^i{}^{2}}} (x_1^i) & \text{if
        } x_1^i\geq \m\\
        \mathcal{N} \LF{\m, \sqrt{\s_+{}^2 + \d x_1^i{}^{2}}} (x_1^i), &
        \text{else}
    \end{cases}
\end{align}

@@

\begin{table*}[htbp!]
    \centering
    \caption{Valeurs des paramètres pour différents modèles. En rouge les
    données aberrantes.}
    \label{tab:val}
    \begin{tabular}{c c c c c c c}\hline\hline

        \rowcolor{gray!15} Modèle & $a$ & $f$ & $\m_1$ & $\s_1$ & $\m_2$ &
        $\s_2$ \\\hline

        3G2M2S$_{\mathrm{SNf}}$ & $0.48 \pm 0.07$ & none & $0.39 \pm 0.07$ &
        $0.56 \pm 0.05$ & $-1.5 \pm 0.1$ & $0.52 \pm 0.09$ \\

        3G2M2S & $0.48 \pm 0.17$ & none & $0.36 \pm 0.08$ & $0.61 \pm 0.05$ &
        $-1.3 \pm 0.2$ & $0.60 \pm 0.12$ \\

        3G2M2SF & \textcolor{red}{$0.1 \pm 0.6$} & \textcolor{red}{$0.2 \pm
        0.6$} & $-0.9 \pm 0.7$ & $0.7 \pm 0.3$ & $0.5 \pm 0.2$ & $0.6 \pm 0.1$
        \\

        3G2M1S & $0.47 \pm 0.07$ & none & $0.35 \pm 0.04$ & $0.61 \pm 0.03$ &
        $-1.25 \pm 0.10$ & $\s_1$ \\

        3G2M1SF & \textcolor{red}{$0.2 \pm 0.9$} & $0.7 \pm 0.3$ & $0.36 \pm
        0.04$ & $0.60 \pm 0.03$ & $-1.23 \pm 0.10$ & $\s_1$ \\

        2G2M2S & none & none & $0.49 \pm 0.04$ & $0.54 \pm 0.03$ & $-0.72 \pm
        0.08$ & $0.83 \pm 0.07$ \\

@@

    \end{tabular} \bigbreak

\begin{tabular}{c c c}\hline\hline

    \rowcolor{gray!15} Modèle & $\m$ & $\s$ \\\hline

@@

\end{tabular} \bigbreak

\begin{tabular}{c c c c c}\hline\hline

    \rowcolor{gray!15} Modèle & $\m$ & $\s_-$ & $\s_+$ \\\hline

@@

\end{tabular} \bigbreak

\begin{tabular}{c c c c c c c c c}\hline\hline

    \rowcolor{gray!15} Modèle & $a$ & $f$ & $\m_1$ & $\s_1$ & $\m_2$ & $\s_2$ &
    $m_3$ & $\s_3$ \\\hline

    3G3M3S & $0.14 \pm 0.08$ & none & $0.51 \pm 0.06$ & $0.54 \pm 0.04$ & $-1.9
    \pm 0.2$ & $0.29 \pm 0.11$ & $-0.55 \pm 0.12$ & $0.67 \pm 0.15$ \\

@@

\end{tabular} \bigbreak

\end{table*}

\section{Results}
To compare all these models, we use the Akaike Information Criterion corrected
for sample size (BURNHAM 2002), that penalises the increase of free parameters
in order to discourage overfitting:
\begin{equation}
    \mathrm{AICc} = \mathrm{AIC} + \LR{2k\LF{k+1}}{n - k - 1}
\end{equation}
with $\mathrm{AIC} = 2k - 2\ln\LF{\mathcal{L}}$, where $k$ is the number of free
parameters and $\Lc$ the likelihood. The probability for a model to be as
representative as the "best" one is given by:
\begin{equation}
    p(\mathrm{other} > \mathrm{best}) = \exp\LF{\D\mathrm{AICc}/2}
\end{equation}
The results are showed table \ref{tab:comp}. We find that every model lacking an
evolution of the stretch with the redshift is systematically worse than those
that implement it.

\begin{table*}[htbp!]
    \centering
    \caption{Comparaison des modèles. NR représente les modèles implémentés
             durant ce stage. (F) indique les modèles pour lesquels il n'y a pas
             d'évolution de la fraction de SNe~Ia jeunes et vieilles en fonction
             du redshift.}
    \label{tab:comp}
    \begin{tabular}{c c c c c c c}\hline\hline

        \rowcolor{gray!15} Name & Description & Free param &
        $\ln\mathcal{L}$ & $AICc$ & $\D AICc$ & Proba \\\hline

        3G2M1S & NR 1S & 4 & 1815 & 1823 & 0.0 & $1.0$ \\

        3G2M2S & NR 2S & 5 & 1815  & 1825 & -2.0 & $3.6\times10^{-1}$ \\

        2G2M2S & Howell & 4 & 1818  & 1826 & -3.4 & $1.8\times10^{-1}$ \\

        3G3M3S & NR 3S & 7 & 1812  & 1826 & -3.6 & $1.6\times10^{-1}$ \\

        3G3M3SF & NR 3S (F) & 8 & 1813 & 1829 & -6.3  & $4.3\times10^{-2}$
        \\

        2G2M2SF & Howell (F) & 5 & 1823  & 1833 & -9.9 & $7.0\times10^{-3}$
        \\

        3G2M1SF & NR 1S (F) & 5 & 1823  & 1833 & -10.4 & $5.5\times10^{-3}$
        \\

        3G2M2SF & NR 2S (F) & 6 & 1823  & 1835 & -12.0 & $2.5\times10^{-3}$
        \\

        1G1M2S & Kessler (F) & 3 & 1837  & 1843 & -20.2 & $4.1\times10^{-5}$
        \\

@@

    \end{tabular}
\end{table*}
